Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-24 prop_iop.tex
prop_letter.tex \section{Kochen-Specker} Improving the bound...

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)\subseteq\left[0,\delta\right]$ ;\\ 
1 & if $\bar{\mu}(P)\subseteq\left[1-\delta,1\right]$
}\end{equation}
is a cryptodeterministic measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
orthogonal events, we must have $N\le d$. 
\begin{itemize}
\item If $\pmeas(P_{i})=0$ for all $i$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
\overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\Rightarrow\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
for $i_{0}\ne i_{1}$, then
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
\end{equation}
which contradicts to definition~\ref{def:delta-deterministic} so
that this case is impossible.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}

>>>>

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)\subseteq\left[0,\delta\right]$ ;\\ 
1 & if $\bar{\mu}(P)\subseteq\left[1-\delta,1\right]$
}\end{equation}
is a cryptodeterministic measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
Without loss of generality, there are two cases:
\begin{itemize}
\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then
\begin{equation}\eqalign{ 
& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
\overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\Rightarrow\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
then
\begin{equation}\eqalign{ 
& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
}\end{equation}
\end{itemize}
Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\frac{1}{3}$.\end{cor}

### 2017-05-24 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Improving the bound...

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by
\begin{equation}
\mu(P)=\begin{cases}
0 & \textrm{if }\bar{\mu}(P)\subseteq\left[0,\delta\right]\textrm{ ;}\\
1 & \textrm{if }\bar{\mu}(P)\subseteq\left[1-\delta,1\right]
\end{cases}
\end{equation}
 is a cryptodeterministic quantum probability measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have\begin{subequations}
\begin{eqnarray}
 &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
\end{eqnarray}
\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
orthogonal events, we must have $N\le d$. 
\begin{itemize}
\item If $\pmeas(P_{i})=0$ for all $i$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\\
 & \overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\\
 & \Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
\end{eqnarray}
\end{subequations}
\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
\end{eqnarray}
\end{subequations}
\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
for $i_{0}\ne i_{1}$, then
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
\end{equation}
which contradicts to definition~\ref{def:delta-deterministic} so
that this case is impossible.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}

>>>>

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by
\begin{equation}
\mu(P)=\begin{cases}
0 & \textrm{if }\bar{\mu}(P)\subseteq\left[0,\delta\right]\textrm{ ;}\\
1 & \textrm{if }\bar{\mu}(P)\subseteq\left[1-\delta,1\right]
\end{cases}
\end{equation}
 is a cryptodeterministic quantum probability measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have\begin{subequations}
\begin{eqnarray}
 &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
\end{eqnarray}
\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
Without loss of generality, there are two cases:
\begin{itemize}
\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
 & \overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\\
 & \Rightarrow & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{eqnarray}
\end{subequations}
\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{eqnarray}
\end{subequations}
\end{itemize}
Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\frac{1}{3}$. \end{cor}
